---
title: "7313 Assignment 3: Modeling"
output:
  html_document:
    toc: TRUE
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)


library(RMySQL)   #MySQL interaction
library(dplyr)    #data handling
library(caret)    #classification and regression training
#library(ggplot2)   #for graphs
library(magrittr)  #for pipes
#library(lubridate)  #for date manipulation
#library(corrgram) #for correlogram 1
#library(corrplot) #for correlogram 2
#library(Hmisc)   #for correlation matrix with p-values
```

\newpage

#Summary:

**Business Use Case**: Predict whether a customer will churn (i.e. whether a customer has only made one purchase). 

During an initial foray into modeling, we trained several models using the following (subset of) variables. 

**Target**: *is_churn*: "1 if customer did NOT return, 0 if customer did return"

**Features**: as defined in "Exploratory Data Analysis" Lab. 


- *home_delivery*: Binary variable (1 if home delivery, 0 if collected in store)
- *num_items_sold*: The number of items included in the order
- *sales*: The total purchase amount in SEK
- ~~*margin*: The store's margin on the order in SEK~~
- ~~*shipping_cost*: How much the customer paid for shipping in SEK~~
- *discount*: If a discount was applied to order
- ~~*flag_unknown*: Binary variable (1 if order contains an item with unknown price, 0 if prices of all products are known)~~
- *flag_multiple*: Binary variable (1 if customer made several purchases the same day, 0 if they did not)
- *num_returns*: Whether or not one or more products in the order have been returned

*(NOTE: the above feature subset was rather arbitrarily chosen at this point)*

**Models Evaluated**: And their Accuracies 

The following models were fitted with the specification of "is_churn ~." with the above features. Every model has an identical train control object that does a 5-fold cross validation. 


| Model Type     | Accuracy |
|----------------|----------|
| Logistic model | 0.5774   |
| LDA model      | 0.5775   |
| QDA model      | 0.4437   |
| CART model     | 0.5808   |
| SVM model      | 0.5774   |
| Random Forest  | 0.5792   |

*(NOTE: We may want to prioritize a different metric over Accuracy later)*


**Final Model** 

Based simply on the accuracy measures of the above models in our initial model evaluation (before feature selection and further fine-tuning), we choose the **CART model**. (This will likely change upon more fine-tuning/ redefining variables/ choosing different features).


\newpage

#Data Preparation: 

##Load datasets:

```{r dataimport, message = F, warning = F}

#establish MySQL connection:
#sql_con = dbConnect(MySQL(), dbname = "ToyStorey", host = "db.cfda.se", 
#                port = 3306, user = "toystorey", password = "toys@sse") 

#SQL query 
#finalquery <- "SELECT Receipt.customer_id, Receipt.date, Receipt.home_delivery, COUNT(ReceiptProduct.receipt_id) AS num_sold_items, IF(Receipt.home_delivery = 1 AND SUM(IFNULL(Product.price, 0)) < 200, 70, 0) AS shipping_cost, SUM(IFNULL(Product.price, 0)) * (IF(Receipt.discount_code = 'MA20GIC', 0.2, IF(Receipt.discount_code = 'M2GI5C', 0.25, 0))) AS discount, SUM(IFNULL(Product.price, 0)) AS sales, MAX(IF(ReceiptProduct.product_id = 99997, 1, 0)) AS flag_unknown, IF(COUNT(DISTINCT Receipt.receipt_id) > 1, 1, 0) AS flag_multiple, SUM(ReceiptProduct.is_return) AS flag_returns, IF(NumPurchasesPerCustomer.num_purchases = 1, 1, 0) AS is_churn FROM Receipt LEFT JOIN Receipt r_before ON (Receipt.customer_id = r_before.customer_id AND Receipt.date < r_before.date)  LEFT JOIN ReceiptProduct ON (Receipt.receipt_id = ReceiptProduct.receipt_id) LEFT JOIN Product ON (ReceiptProduct.product_id = Product.product_id) LEFT JOIN NumPurchasesPerCustomer ON NumPurchasesPerCustomer.customer_id = Receipt.customer_id WHERE r_before.date IS NULL GROUP BY Receipt.customer_id;"
  
#fetch the results and save as df
#df_churn <- fetch(dbSendQuery(sql_con,finalquery), n=-1)

#or Load Adam's churn dataset directly from csv:
df <- read.csv("C:/Users/nickp/Documents/7313DataAnalysis/churn.csv")

#keep target and subset of feature variables: (feature selection later?)
df_churn <- df[,c("is_churn","home_delivery","num_items_sold","sales","discount","flag_multiple","num_returns")]
#df_churn <- df[,c("is_churn","home_delivery","num_items_sold","sales","margin","discount","flag_unknown","flag_multiple","num_returns")]
#df_churn <- df[,c("is_churn","home_delivery","num_items_sold","sales","shipping_cost")]

#make sure target variable is factor (for classification models; for regression models, not needed):
df_churn$is_churn %<>% as.factor()

```

##Split into training/test:

Split data into training and test set:

```{r}

set.seed(7313)
#partition the data evenly along the dependent variable: 70% will be training, 30% testing
training.indices <- createDataPartition(df_churn$is_churn, p = 0.7, list = F)

#training data set
churn_train <- df_churn[training.indices,]

#testing data set
churn_test <- df_churn[-training.indices,]

#Sum of churn in training set:
#sum(churn_train$is_churn %>% as.numeric())


```

#Logistic Model

##With "stats" package:

Train a basic linear logistic regression with package **stat**'s "glm":

```{r}

#fit logistic regression
glm.fit = glm(is_churn~., 
              churn_train, 
              family = binomial)
#summary(glm.fit)

## EVALUATION 
#make prediction of the model on train data:
pred = as.factor(ifelse(predict(glm.fit, churn_train, type = "response") > 0.5, 1, 0))
#pred = predict(glm.fit, churn_train, type = "response")
#hist(pred)

#create "confusion matrix": Calculates a cross-tabulation of observed and predicted classes with associated statistics.
acc.test = confusionMatrix(pred , churn_train$is_churn)
acc.test
```

##With "caret" package

Same thing, but with **caret**'s "train":

```{r}

#train a logistic model with caret:
churn_glm_model = caret::train(
  form = is_churn ~.,
  data = churn_train,
  trControl = trainControl(method = "cv", number = 2),   #number kfold valid. change test control object here:
  method = "glm",   #linear logistic model (Change this later)
  family = "binomial"
)

## EVALUATION 
#make predictions, using the generated model, on train data
#churn_glm_prediction <- predict(churn_glm_model, churn_train)   #default .50 cutoff
churn_glm_prediction = as.factor(ifelse(predict(churn_glm_model$finalModel, churn_train, type = "response") > 0.5, 1, 0))   #custom cutoff

#create "confusion matrix": Calculates a cross-tabulation of observed and predicted classes with associated statistics.
glm.cm <- confusionMatrix(churn_glm_prediction, churn_train$is_churn)
glm.cm

```


**Interpretation of Confusion Matrix**:

Here is a wikipedia article that shows the formulas for calculating the relevant measures from the confusion matrix: https://en.wikipedia.org/wiki/Sensitivity_and_specificity

    -  true positive (TP): eqv. with hit
    -  true negative (TN): eqv. with correct rejection
    -  false positive (FP): eqv. with false alarm, Type I error
    -  false negative (FN): eqv. with miss, Type II error
    -  sensitivity or true positive rate (TPR): eqv. with hit rate, recall. TPR = TP / P = TP / (TP+FN)
    -  specificity (SPC) or true negative rate. SPC = TN / N = TN / (TN+FP)
    -  precision or positive predictive value (PPV).  PPV = TP / (TP + FP)
    -  negative predictive value (NPV).  NPV = TN / (TN + FN)
    -  fall-out or false positive rate (FPR).  FPR = FP / N = FP / (FP + TN) = 1-SPC
    -  false negative rate (FNR).  FNR = FN / (TP + FN) = 1-TPR
    -  false discovery rate (FDR).  FDR = FP / (TP + FP) = 1 – PPV
    -  accuracy (ACC).  ACC = (TP + TN) / (TP + FP + FN + TN)


##Change cutoff (for classification)

**Can you improve the model by lowering the cutoff?**

We can vary the cutoffs in glm model and plot the accuracies:

```{r}

cutoffs <- seq(0.4,0.6,0.025)
accuracy <- NULL  #initialize accuracy
for (i in 1:length(cutoffs)){
  cutoff <- cutoffs[i]
  #Predicting for cut-off, confusion matrix
  prediction <- ifelse(glm.fit$fitted.values >= cutoff, 1, 0)
  cm <- confusionMatrix(prediction %>% as.factor(), churn_train$is_churn %>% as.factor())
  #add to accuracy vector
  accuracy <- c(accuracy, cm$overall["Accuracy"])   #can access different metrics (specificity, etc) in cm object
}

plot(cutoffs, accuracy, pch =19,type='b',col= "steelblue",
     main ="Logistic Regression, accuracy vs. cut-off", xlab="Cutoff Level", ylab = "Accuracy %")

```

##Evaluate on Test data:

Finally we want to evaluate the performance using unseen data, the test set. 

```{r}

#make prediction of the model on test data:
pred.test = as.factor(ifelse(predict(glm.fit, churn_test, type = "response") > 0.45, yes = 1, no = 0))
confusionMatrix(data = pred.test, reference = churn_test$is_churn)


#Same thing, but with "Caret"

#make predictions, using the generated model, on train data
churn_glm_prediction2 = as.factor(ifelse(predict(churn_glm_model$finalModel, churn_test , type = "response") > 0.45, 1, 0))
#create "confusion matrix": Calculates a cross-tabulation of observed and predicted classes with associated statistics.
confusionMatrix(churn_glm_prediction2, churn_test$is_churn)

```

#Other models using caret:

See a list of models available in R package for classification and regression training *caret* (and their tuning parameters) [here](https://topepo.github.io/caret/available-models.html):

Various methods of estimating model accuracy with caret [here](https://machinelearningmastery.com/how-to-estimate-model-accuracy-in-r-using-the-caret-package/). (Note in the following models we just use k-fold cross validation with 5 subsets).

Tuning the "trainControl" object [here](https://rdrr.io/cran/caret/man/trainControl.html).

##LDA and QDA model:


[Linear discriminant analysis](https://en.wikipedia.org/wiki/Linear_discriminant_analysis): 

```{r}

set.seed(4145)

#train a LDA model with caret:
churn_LDA_model = caret::train(
  is_churn ~.,
  data = churn_train,
  trControl = trainControl(method = "cv", number = 5),   #5 kfold valid. 
  method = "lda"   #LDA
)

#train a QDA model:
churn_QDA_model = caret::train(
  is_churn ~.,
  data = churn_train[,-c(6)],  #get rid of cols causing rank deficiency
  trControl = trainControl(method = "cv", number = 5),   #5 kfold valid. 
  method = "qda"   
)

#Posterior probabilities (odds that each entity is a 0/1)
lda.post.prob <- churn_LDA_model %>% predict(churn_test, type="prob")
qda.post.prob <- churn_QDA_model %>% predict(churn_test, type = "prob")

#Predicted classes:
lda.pred.churn <- churn_LDA_model %>% predict(churn_test)
qda.pred.churn <- churn_QDA_model %>% predict(churn_test)

# LDA model Accuracy rate on test data
#mean(lda.pred.churn == churn_test$is_churn)

#confusion matrix:
lda.cm <- confusionMatrix(lda.pred.churn, churn_test$is_churn)
lda.cm
qda.cm <- confusionMatrix(qda.pred.churn, churn_test$is_churn)
qda.cm

```



```{r, eval = F}
#Plot of LDA with missclasified churners (NOTE this works better with fewer, non-binary features:

#generate column for "correct prediction"
ldachurn_test <- churn_test
ldachurn_test$correct.pred = lda.pred.churn == ldachurn_test$is_churn

#random subset (more plottable)
ldachurn_test %<>% dplyr::sample_n(1000)

#plot of two variables and correct class:
qplot(sales, num_returns, data=ldachurn_test, cex=2, col=is_churn)
#plot of same vars and whether was correct predition:
qplot(sales, num_returns, data=ldachurn_test, cex=2, col=correct.pred)

```


##CART model:

[Classification And Regression Tree (CART)](https://machinelearningmastery.com/classification-and-regression-trees-for-machine-learning/).

**Using package Caret**

```{r}

set.seed(4145)

#train a CART model with caret:
churn_CART_model = caret::train(
  form = is_churn ~.,
  data = churn_train,
  trControl = trainControl(method = "cv", number = 2),   #number kfold valid. 
  method = "rpart"  #,   #CART
  #control = rpart.control(minsplit = 1, minbucket = 1, cp = 0.01)#,   #control object for rpart
  #tuneLength = 10   #number of possible cp values to evaluate: (cp = complexity parameter; penalizes tree for having too many splits) -- optimizes pruning
)    


plot(churn_CART_model)  #view complexity parameter values
churn_CART_model$bestTune    #best cp value

#View the final tree:
par(xpd = NA) # Avoid clipping the text 
plot(churn_CART_model$finalModel)
text(churn_CART_model$finalModel,  digits = 3)

# Make predictions on the test data
cart.pred.churn <- churn_CART_model %>% predict(churn_test)
# CART model accuracy rate on test data
#mean(cart.pred.churn == churn_test$is_churn)

#create confusion matrix:
cart.cm <- confusionMatrix(cart.pred.churn, churn_test$is_churn)
cart.cm

#Source: http://www.sthda.com/english/articles/35-statistical-machine-learning-essentials/141-cart-model-decision-tree-essentials/

```

**Using Package rpart**

```{r}

#caret automatically prunes tree. For more control use rpart:
#Train a tree with package rpart:
library(rpart)
library(rpart.plot)
prune.control = rpart.control(minsplit = 10, minbucket = 10, cp = 0.001)
churn_rpart_model <- rpart::rpart(
  form = is_churn ~.,
  data = churn_train,
  control = prune.control)
rpart.plot(churn_rpart_model) #plot of manually-tuned tree

```



##Support Vector Maching (SVM)

[Support vector machine](https://en.wikipedia.org/wiki/Support-vector_machine)  

*Does not scale well* -- use a subset! 


```{r}

#random sample of 10000 rows:
svm_sample <- dplyr::sample_n(churn_train, 10000)

#reclassify target:
levels(svm_sample$is_churn) <- c("no_churn","churn")

#train SVM
churn_svm_fit = train(
  is_churn ~.,
  data = svm_sample,
  trControl = trainControl(method = "cv", number = 5, savePred = T, classProb = T),    #save predictions and class probs
  method = "svmLinear"   #svm model
)


# Make predictions on the test data
svm.pred.churn <- churn_svm_fit %>% predict(churn_test)

#reclassify target:
levels(svm.pred.churn) <- c("0","1")

#create confusion matrix:
confusionMatrix(svm.pred.churn, churn_test$is_churn)
```



#Bagging, Boosting, Random Forests:

Regression and classification trees (CART above, e.g.) have pros and cons:
Pros: 

- very intuitive
- mirror human behavior (more than other regression/classification)
- conducive to graphics, can be interpreted by anyone
- don't need dummy variables

Cons:

- lower predictive accuracy than other methods
- not robust (classifications are susceptible to minor changes in the data)

To improve these trees' predictions, you can use bagging, random forests, and boosting. (ISLR 315)


##Bagged Tree:

Simple Decision trees suffer from high variance -- repeating a training with new training data can give you a very different tree. **Bootstrap aggregation**, or bagging, is a general method for reducing variance of a statistical learning method (not just for decision trees).

To reduce the variance (and thus increase prediction accuracy) of a statistical learning method, you can take many training sets from a population, build separate prediction models, and average the resultant predictions. Since we do not have multiple training sets, we simply **bootstrap**, or take repeated samples (B different bootstrapped training data sets) from our one training set, including all p predictors. (ISLR 316)

Bagging is particularly useful for decision trees. These trees are deep (long paths, root to leaf) and are not pruned (many nodes). Every tree thus has high variance (may not match other trees with different trains) and low bias (fits data well). You reduce the variance by averaging all of the trees. With regressions, the "average result" is an average. With classifications, the "average result" is some sort of *majority vote* between the B-many trees ("Is it a 1 or 0?"). (ISLR 317)

**However**, even though we have a lower-variance/higher-accuracy tree, The bagged tree is less interpretable: There is no easy way to represent a *single* tree because the bagged tree is an 'average'. In order to determine variable importance in bagged trees, you can use *RSS* (regression trees) or *Gini index* (classification trees). (ISLR 319)

##Random Forest:

Random forests tweaks the method of bagged trees. They start the same way: buildign multiple trees using bootstrapped training samples. However, instead of using all p predictors, we use a random subset of m (m<p) predictors as split candidates. Each bootstrap sample uses a different m subset. (The default m is sqrt(p), e.g. a subset of 4 random variables out of 14 total. When m=p, a random forest is merely a bagged tree). 

Only allowing a smaller subset of splits prevents all trees from being highly correlated with each other---for instance, if all the p-variable bagged trees have the same strong-predictor first 'split', then their average won't reduce variance that much. Randomly subsetting variables (possible splits) prevents that, as some trees won't have the same first split. This is thus a *decorrelation* of the bagged trees.

Tuning a random forest using caret: https://machinelearningmastery.com/tune-machine-learning-algorithms-in-r/


```{r}


set.seed(123)

library(parallel)
library(doParallel)

start.time <- Sys.time()  #measure how much time it takes

#register cluster
cluster <- makeCluster(detectCores() - 1) # convention to leave 1 core for OS
registerDoParallel(cluster)

#Tune it better with: https://rpubs.com/phamdinhkhanh/389752

levels(churn_train$is_churn) <- c("0","1")
churn_RF_model <- caret::train(is_churn~., 
                      data=churn_train, 
                      method='rf', 
                      ntree = 2,
                      trControl=trainControl(method='cv', number=2) )

#de-register parallel processing cluster:
stopCluster(cluster)
registerDoSEQ()     #forces R to return to single-thread processing

#measure passed time:
end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken

#View how Accuracy changes with number predictors
plot(churn_RF_model)

#View final model:
plot(churn_RF_model$finalModel)

# Make predictions on the test data
rf.pred.churn <- predict(churn_RF_model,churn_test)


#create confusion matrix:
RF.CM <- confusionMatrix(rf.pred.churn, churn_test$is_churn)
RF.CM

```


##Boosted Tree:

Boosting can be generally applied; here, it is applied to trees.

In boosting, 

- the full training data is used at once (no bootstrapping)
- trees are grown *sequentially*: Every subsequent tree is grown using information from previous trees

Instead of hard-fitting the data to a tree all at once (which can cause over-fitting), boosting learns slowly. Subsequent fitting is done to the *residuals* (not the outcome Y) of of the current model, and the new decision tree is incorporated into the fitted function, updating the residuals.  (ISLR 321)

Tuning parameters:

- **number of trees B:** can over-fit if too large! (Unlike bagging/RF). Use cross-validation to select.
- **shrinkage parameter $\lambda$:** a small positive number to control how fast it learns (~0.01 or 0.001)
- **number of splits in each tree d:** often d=1 (a "stump"), where boosting is then an additive model, adding one variable at a time. Otherwise, d might be used as *interaction depth*.

With R **caret**, you can use method = "ada".


#Feature selection:

##Subset Selection:

Choosing a subset of the predictors.

**Best Subset Selection**: Fitting a separate least squares regression for *every* possible combination of the *p* predictors, totaling $2^p$ models. Fit all the (two, three... p)-variable models, choosing the best for each number of variables ("best" = smallest RSS). You thus have p-many models with different numbers of predictors.  Then, select the best out of all the different-many variable models (here "best" = AIC/BIC/adjusted $R^2$... you can't use RSS when there are different numbers of variables because it will choose the model with all variables -- the best one-variable model will always underperform the all-variable model in RSS). Computationally demanding! (ISLR 205)

**Forward stepwise selection**: Start with the null model with no predictors, then add one predictor at a time, selecting the best (smallest RSS/ highest $R^2$) at each step. You thus have p-many models with different numbers of predictors. Then, choose the best model out of all the different-many variable models (here "best" = AIC/BIC/adjusted $R^2$... you can't use RSS when there are different numbers of variables because it will choose the model with all variables). Computationally advantageous, but not guaranteed to get the "best" model if a different subset of predictors is used in higher-variable models than in lower-variable models, since you "build it up" one variable at a time. (ISLR 207)


**Backward stepwise selection**: Same as forward, but start with all predictors, removing the least useful predictor. (ISLR 208)


##Shrinkage methods: Lasso and Ridge Reduction

Keeping all of the predictors, but *constraining* or *regularizing* their coefficient estimates towards zero. (Note: Lasso can constrain all the way to zero, effectively becoming a subset selector).

**Ridge Regression:** Instead of simply minimizing the RSS as in standard least squares fitting, we minimize $RSS + \lambda \sum_{j=1}^{p} \beta_j^2$, where $\lambda \geq 0$ is a *tuning parameter*, separately determined, and the whole second term ($\lambda \sum_{j=1}^{p} \beta_j^2$) is a *shrinkage penalty*. When $\lambda$ equals 0, there is no penalty, and the ridge regression approaches least squares. As $\lambda$ approaches infinity, the coefficients for the p predictors approach 0. Coefficients are determined for every value of $\lambda$. The shrinkage penalty is *not* applied to the intercept (the mean value when other coefficients are zero). (ISLR 215)

Advantage over least squares: Ridge regression gives control over the bias-variance tradeoff. Increasing $\lambda$ decreases the flexibility of the of the regression fit, thus lowering variance but increasing bias. It therefore helps prevent overfitting training data. 

**Lasso:** Ridge regression doesn't allow any of the p predictors' coefficients to be zero, so the model still has all variables and is rather un-interpretable. Lasso is generally the same approach as Ridge Regression (includes a penalty term and tuning parameter), but the formula (minimize $RSS + \lambda \sum_{j=1}^{p} |\beta_j|$) now allows coefficients to be zero, effectively subsetting the features and allowing for more interpretable models. (ISLR 219)

http://www.sthda.com/english/articles/37-model-selection-essentials-in-r/153-penalized-regression-essentials-ridge-lasso-elastic-net/

https://web.stanford.edu/~hastie/glmnet/glmnet_alpha.html


```{r ridgeLasso, warning=F, message = F}

library(glmnet)

#adapted from: https://drsimonj.svbtle.com/ridge-regression-with-glmnet

#Data Preparation:
#create matrix of predictors (remove the target, save as data matrix)
x.train <- churn_train[,-c(1)] %>% data.matrix()
x.test <- churn_test[,-c(1)] %>% data.matrix()
#turn target into numeric
y.train <- churn_train[,c(1)] %>% as.numeric()  
y.test <- churn_test[,c(1)]

#can specify grid of lambdas to search over:
#lambdas <- 10^seq(3, -2, by = -.1)
#Alpha = 0 for Ridge Regression
#rr <- glmnet(x.train, y.train, alpha = 0, family = "binomial", type.measure = "class", lambda = lambdas)
#Alpha = 1 for Lasso
#lasso <- glmnet(x,y, alpha = 1, lambda = lambdas)
#NOTE: you can set Alpha between 0 and 1 for "elastic net regression""

#find optimal Lambdas using built-in cross validation (CV) function:
#Ridge Regression (alpha = 0)
rr_opt <- cv.glmnet(x.train, y.train, alpha = 0)
rr_opt_lambda <- rr_opt$lambda.min   #lowest point = optimal lambda (best minimized error under cross validation)
#Lasso (alpha = 1)
lasso_opt <- cv.glmnet(x.train, y.train,  alpha = 1)
lasso_opt_lambda <- lasso_opt$lambda.min

#View the lambda plots agains MSE:
plot(rr_opt)
plot(lasso_opt)

#create model with best lambda, then use that model to predict
model.rr <- glmnet(x.train, as.factor(y.train), alpha = 0, family = "binomial", type.measure = "class", lambda = rr_opt_lambda)
predict.rr <-predict(model.rr,   #model 
                     newx = x.test,  #new x values to test
                     type="class",
                     s = rr_opt_lambda)  #use optimum lambda
model.lasso <- glmnet(x.train, as.factor(y.train), alpha = 0, family = "binomial", type.measure = "class", lambda = lasso_opt_lambda)
predict.lasso <-predict(model.lasso,  
                     newx = x.test,
                     type="class",
                     s = lasso_opt_lambda)  

#turn predictions into factors and make sure same levels...
predict.rr %<>% as.factor()
predict.lasso %<>% as.factor()
levels(predict.rr) <- c("0","1")
levels(predict.lasso) <- c("0","1")

#View the accuracies of Ridge Regression/ Lasso models:
confusionMatrix(predict.rr, y.test)
confusionMatrix(predict.lasso, y.test)


```


##Dimension Reduction (PCA): 

The methods above control variance by eliminating/restricting the original predictor variables. The following method(S) *transforms* the predictors (creating "new" predictors with linear combinations of the original p predictors), then uses least squares. This is called *Dimension reduction*. (ISLR 228)

One dimension reduction method is *Principal Components Analysis* (PCA), an unsupervised learning technique that reduces the dimension of an n x p matrix X. 

**First principal component**
This method first finds the axis/direction of the data that has the highest variance, the *first principal component*. This will be a line that is closest to all n of the observations (a line of best fit). It is given by the formula:

$$Z_1 = \phi_1 (x_1 - \overline{x_1}) + \phi_2 (x_2 - \overline{x_2})$$

The data are projected onto this axis, creating a linear combination of the (two) data features with the highest variance out of all possible linear combinations (that is, all linear combinations where $\phi_1^2 + \phi_2^2 =1$, or else you can arbitrarily choose high coefficients for high variance). The results of this linear combination are called *z-scores* (each data point will have a z-score showing how far from the mean $x_1$ and $x_2$ the point is, *along that axis*). Thus, these z-scores are essentially single-number summaries of both predictors for each point.


**Second (Third, fourth...) principal component**
Then, we can find a second principal component ($Z_2$) by finding linear combinations of variables that are uncorrelated with our first component $Z_1$ and has highest variance. It will be orthogonal to the previous prior component. With only two variables, two components is maximum, but you can otherwise build up subsequent components by finding linear combinations with maximum variance combinations subject to the fact that it is uncorrelated with prior components. We can find up to p principal components with p predictors (though if we use all p principal components, it's not really "dimension reduction" is it).

```{r}
#interesting page with visuals: https://www.datacamp.com/community/tutorials/pca-analysis-r

#Data Preparation:
#remove the target (and other vars?)
x.train <- churn_train[,-c(1)]
x.test <- churn_test[,-c(1)]

#PCA on training set (minus target!)
pca_train <- prcomp(x.train, scale = T)
#calculate variance
pca_train$var <- pca_train$sdev^2
#how much variance explained by each component
pve <- pca_train$var/sum(pca_train$var)
pve   
#graph of cumulative sum of variance explained by each PC
plot(cumsum(pve), xlab = "Principal Component", ylab = "Cum. Prop. of Var. Explained")

```

We can train a model using principal components as features, and compare how this model does against previous models:

```{r}

#new training set has y var and pca-x vars:
train.data <- data.frame(is_churn = churn_train$is_churn, pca_train$x)

#apply whatever model to pca-transformed training data
#train a CART model with caret:
cart.pca = caret::train(
  form = is_churn ~.,
  data = train.data,
  trControl = trainControl(method = "cv", number = 2),   #number kfold valid. 
  method = "rpart"
)

#transform test set into PCA-vars using SAME transformation (even if not "max" variance for the test set):
pca_test <- predict(pca_train, newdata = x.test)  #note "pca_train" is a transformation pca-object that contains lots of things
pca_test %<>% as.data.frame()

#make prediction on pca-transformed test data
cart.predict.pca <- predict(cart.pca, pca_test)
  
#compare model results from pca / no-pca
cart.cm.pca <- confusionMatrix(cart.predict.pca, churn_test$is_churn)
cart.cm.pca

#compare to LDA (no PCA)
cart.cm

#When applied to CART, gets better accuracy. with LDA, it gets worse accuracy?
```

Doing the same, but within "caret" package:

```{r, eval = F, echo = F}

#To inclue PCA within caret "Train", use preProcess! 

#create a pre-processing transformation object
preProc <- preProcess(churn_train[,c(-1)], #don't include target
                      method = c("pca"),   #can also center/scale/etc
                      pcaComp = 3)  #how many PCA components to keep (up to "p")

#apply (same) preprocessing to both train and test sets (minus target):
train.pca <- predict(preProc, churn_train[,c(-1)])
test.pca <- predict(preProc, churn_test[,c(-1)])
#add the target variable back:
train.pca$is_churn <- churn_train$is_churn
test.pca$is_churn <- churn_test$is_churn

#(whatever) model with PCA
cart.pca1 = caret::train(
  form = is_churn ~.,
  data = train.pca,  #use transformed training data
  trControl = trainControl(method = "cv", number = 2),   
  method = "rpart"
)
pred <- predict(cart.pca1,test.pca)
cm.pca <- confusionMatrix(pred, test.pca$is_churn)

#same model without PCA
cart.nopca1 = caret::train(
  form = is_churn ~.,
  data = churn_train,   #use original training data
  trControl = trainControl(method = "cv", number = 2),   
  method = "rpart"
)

#view accuracy with / without PCA  (on train data)
pred <- predict(cart.nopca1,churn_test)
cm.noPca <- confusionMatrix(pred, churn_test$is_churn)

#Compare Accuracies:
cm.pca
cm.noPca

```


#Deep Learning:

##eXtreme Gradient Boosting tree (XGBoost)

TODO better notes...

Try to get rid of errors in previous iterations, and want to minimize loss. Where do we find errors, and how can I change the tree to minimize loss in each new iteration of model?

FAST: it uses **gradient descent algorithm**. Calculate partical derivatives to find minima of loss function (RSS). It starts at a random point and takes a step, evaluating if higher or lower. Once it finds a local minimum, it continues for a few more steps to see if it is the true minimum (or just a local minimum). Therefore it optimizes the loss function.

Overview:

- good when there is lots of training data
- good with numeric or numeric-and-cateogorial features (bad with just categorical fields)
- not good for NLP
- not good with small datasets

Read about extreme gradient boosting with  [here](https://datascienceplus.com/extreme-gradient-boosting-with-r/).

From source: *"xgboost shines when we have lots of training data where the features are numeric or a mixture of numeric and categorical fields. It is also important to note that xgboost is not the best algorithm out there when all the features are categorical or when the number of rows is less than the number of fields (columns)."*


```{r, eval = F}

#one tutorial here: https://www.hackerearth.com/practice/machine-learning/machine-learning-algorithms/beginners-tutorial-on-xgboost-parameter-tuning-r/tutorial/


#Define Grid to search over
#These contain all the hyper-parameters (see hackerearth link for explanation)
#Use these to Tune!
xgbGrid <- expand.grid(nrounds = c(50,100),    #max number iterations (sim. to num trees grown)
                       max_depth = c(2,4,6),   #depth of tree
                       colsample_bytree = seq(0.5, 0.9, length.out = 5),    #number of features supplied to a tree
                       eta = 0.1,   #learning rate: usually between 0.01-0.3
                       gamma=0,    #controls regularization / prevents overfitting
                       min_child_weight = 1,   #number of instances needed in child node
                       subsample = 1   #number of samples supplied to a tree 
                      )

##Model TRAINING
#train the model
churn.xgbtree.model <- train(
  is_churn ~.,
  data = churn_train,
  method ="xgbTree",
  trControl = trainControl(method = "cv", number = 2, allowParallel = TRUE),
  tuneGrid = xgbGrid)    

#best hyperparameter values:
churn.xgbtree.model$bestTune


## Model EVALUATION 
#run predictions and evaluate, on both train and test data:
#create "confusion matrix": 
xgbtree.train.cm <- confusionMatrix(predict(churn.xgbtree.model, churn_train) , churn_train$is_churn)  
xgbtree.train.cm
xgbtree.test.cm <-  confusionMatrix(predict(churn.xgbtree.model, churn_test) , churn_test$is_churn)
xgbtree.test.cm

```


##Shallow Neural Network

R's **nnet** does a shallow NN (one hidden layer).

Neural Networks: Neurons are linked, and we don't know how they're linked, but they send signals through different layers.
Input layer: Features. (Three input neurons/features in her example)
Hidden layer: (if many layers, then deep learning)  (one hidden neuron in her example, adjusted)
Output layer: Target
[Tensorflow Playground](https://playground.tensorflow.org/)

```{r}

#library(nnet)   #simple, one-hidden-layer neural network

#Grid of tuning parameters:
#(for brute-force grid search hyperparameter tuning; else can use random search)
nnetGrid <- expand.grid(.decay = c(0.1,  0.5), #regularization parameter (prevent over-fitting)
                        .size = c(2,3))  #how many units are in the (single) hidden layer

##Model TRAINING
#train the model
churn.nnet.model <- train(
  is_churn ~.,
  data = churn_train,
  method ="nnet",
  trControl = trainControl(method = "cv", number = 2, allowParallel = TRUE),
  tuneGrid = nnetGrid,
  verbose = T)  #print iterations or not?

#can specify maxiter = X for max iterations
#note: can always add "metric = ROC" instead of default accuracy, need to also specificy in trainControl "summaryFunction = twoClassSummary"

#Model evaluation:
nn.train.cm <- confusionMatrix(predict(churn.nnet.model, churn_train) , churn_train$is_churn)  
nn.train.cm
nn.test.cm <- confusionMatrix(predict(churn.nnet.model, churn_test) , churn_test$is_churn)  
nn.test.cm

```


